# Chapter 2

*Describe the work you have done this week and summarize your learning.*

This week I have read some data from the internet and created a subset from that data with Rstudio and uploaded it into my GitHub repository. I have learned to analyse my dataset with some simple regression analysis and linear modeling. I have also learned to view my data graphicly with libraries GGally and ggplot2.

Report:

I can read my file as follows:

```{r}
learning <- read.csv("data/learning.csv", sep = ",", header = T)
dim(learning)
str(learning)
```

I named my dataset as learning. It has 7 variables and 166 observations.

Variable attitude represents students attitude.
Variable deep represents students deep learning skills.
Variable stra represents students strategic learning skills.
Variable surf represents students surface learning skills.

All variables above are scaled back to scale 1-5 by taking a mean from a question set in question.

Variables gender and age are self explanatory.
Variable points is a sum of points from an exam. Observations where points < 1 are left out from this subset.

Variables can be seen in a scatterplot (excluding gender) as follows:

```{r}
pairs(learning[-1], col = learning$gender)
```

In scatterplot genders are shown with different colors, red being female and black being male.

If we use libraries GGally and ggplot2 we can see some more detailed information about variables.

```{r}
library(GGally)
library(ggplot2)

p <- ggpairs(learning, mapping = aes(col = learning$gender), lower = list(combo = wrap("facethist", bins = 20)))
p
```

Now we choose three variables that explains variable points most likely. We choose variables that has highes absolute value of correlation with points; attitude, stra and surf.

```{r}
my_model <- lm(points ~ attitude + stra + surf, data = learning)
my_model
```

It seems like attitude explains most points and surf correlates slightly negatively with points.



